Species turnover reveals hidden effects of decreasing Nitrogen deposition in mountain hay meadows

### 2018-06-25 Manuscript.Rmd
Abbildungslegene korrigiert.

```{r cl, fig.cap="Colonization (a) and local survival (b) of oligotrophic (indicator value for nutrients <3; red line) and eutrophic (indicator value for nutrients >3) species along the Nitrogen deposition gradient. Given are means and 95\\%-Credible Intervals from logistic linear mixed models. The vertical lines indicate the deposition rate with equal colonization or survival probabilities for oligotrophic and eutrophic species with the solid line indicating the median and the dashed lines the 5\\% and 95\\% quantiles of the marginal posterior distribution."}
X <- 1:30
Xsd <- (X - 10) / 10

>>>>

```{r cl, fig.cap="Colonization (a) and local survival (b) of oligotrophic (indicator value for nutrients $<3$; red line) and eutrophic (indicator value for nutrients $>3$) species along the Nitrogen deposition gradient. Given are means and 95\\%-Credible Intervals from logistic linear mixed models. The vertical lines indicate the deposition rate with equal colonization or survival probabilities for oligotrophic and eutrophic species with the solid line indicating the median and the dashed lines the 5\\% and 95\\% quantiles of the marginal posterior distribution."}
X <- 1:30
Xsd <- (X - 10) / 10
